% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text
                                   

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 
\usepackage{fontawesome}

\begin{document}

\header{Shrishail}{ Mashal}           % Your name

\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{contact}\small
Laxmi Nivas,
Near Deccan paper mills,
hadapsar railway station 
Pune-411014
India
~
+91 9923738994
~
shrimashal@gmail.com
~
%
\section{links}
Github ID:
\faGithub { shree94mashal}
~
LinkedIn:
\faLinkedin { shrishail-mashal-76a6108a}
~
%
\section{languages}
English Flunces
%
\section{programming}
Python, Shell Scripting,
PHP, JavaScript, HTML
%
\section{operating systems}
Linux, Unix, MacOS
%
\section{DevOps - Containers}
Docker, Docker Swarm, 
Kubernetes
%
\section{DevOps - Cloud}
AWS (Amazon Web Services)
%
\section{DevOps - Automation (Config, Infra)}
Ansible, SaltStack, Vagrant
%
\section{DevOps - Monitoring and VCS}
SVN, Git, GitLab, Newrelic, Monit, Nagios
%
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------
\entry
  {2015--Now}
  {Xento Systems}
  {Pune, IN}
  {\jobtitle{DevOps Engineer}
  
  \begin{itemize}
  \item NewRelic Monitoring Tool Certified Engineer.
  \item Working on Dockerizing internal tools and Configuration management.
  \item Configuring monitoring tools like ELK, Monit, Newrelic for real-time alerts.
  \item Automation of release process using Jenkins Pipeline (CI and CD)
\item Implementation of Vagrant  Saltstack for dev, QA, Stage Production environment
\item Developed scripts for configuration, build, deployment, maintenance, Release etc using PHP
\item Migration of the entire Entrata code base from PHP 5.5 to PHP 7
\item Developed PowerCLI/PowerShell scripts to automate configuration of local into developer machine and virtual machine inventory.
 
  \end{itemize}
  }
\end{entrylist}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------

\entry
{2009--2012}
{Bachelor In Computer Application {\normalfont C.B. K College, Akkalkot [69.00]}}
{Solapur University, Solapur}
{\vspace{-0.3cm}}
%-------------------------------------------------
\entry
{2012--2015}
{Masters In Computer Application {\normalfont Sinhgad Institutes, Pune [69.00]}}
{Pune University}
{ }
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	B.E. Coursework
%----------------------------------------------------------------------------------------
\section{graduate coursework}

\begin{entrylist}
%------------------------------------------------
\entry
{2015}
{Work Order Management} 
{Pune University}
{ Water Tank supply, maintenances management system . \\
  \textbf{Tools and Technolgies:} 1, Core Java 2, Oracle 11g}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL PROJECTS
%----------------------------------------------------------------------------------------
\section{Personal Strengths }

\begin{entrylist}
%------------------------------------------------
\entry
{}
{Excellent analytical, technical and communication skills.}
{ }
{Can easily build up a good rapport with co-workers. Excellence in Communication, good adjusting power to circumstances. Good grasping power, commitment to complete work, Eager to learn new things.}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------
\section{Objectives}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{ Leaning and Exploring  } 
{}
{ To work with an organization that will provide me with a good working environment, opportunity to learn new things. Moreover to be an employee helpful for organization and myself too.
} {}
%------------------------------------------------
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{ The above statements are true to the best of my knowledge and belief.} 
{}

%------------------------------------------------
\end{entrylist}
\begin{flushright}  
\section{shree}
\end{flushright}
\end{document}
